### 2017-02-20 IROS17/intro.tex
Added a lot of images to the paper.

\begin{figure}
\centering
\begin{overpic}[width=0.95\columnwidth]{IntroSwarmPic.pdf}\end{overpic}
\caption{\label{fig:IntroPic}
Swarm of kilobots programmed to move toward the brightest light source as explained in Sec.  \ref{sec:expResults}. The current covariance ellipse and mean are shown in red, the desired covariance is shown in green.  Navigating a swarm using global inputs is challenging because each member receives the same control inputs. 
This paper focuses on using boundary walls and wall friction to break the symmetry caused by the global input and control the shape of a swarm. See multimedia attachment for overview of the experiments.} \vspace{-1em}
\end{figure}

@@

>>>>

@@

\begin{figure}
\centering
\begin{overpic}[width=0.47\columnwidth]{twoRobotRegion.pdf}\end{overpic}
\begin{overpic}[width=0.5\columnwidth]{Reflection.pdf}\end{overpic}
\caption{\label{fig:IntroPic}
All the robots get shared control input. Here in the left picture the wall has infinite friction. Therefore, when the first robot is touching the wall, the second robot can move to anywhere in the shaded area. We introduce a dynamic algorithm to find the shortest path the robots can move to get to their goal positions. Consider the reflection of the goal position to the wall that is aimed to be touched by one of the robots. In the right picture, it is shown that the shortest path with three moves is the straight line between the starting position of the robot and the reflection of the goal.
} \vspace{-1em}
\end{figure}

### 2017-02-20 IROS17/theory.tex
Added a lot of images to the paper.

\section{Algorithms}\label{sec:algorithms}
\subsection{Position Control of Two Robots Using Wall Friction}\label{sec:PostionControl2Robots}
\begin{figure*}
\centering
\renewcommand{\figwid}{0.32\columnwidth}
{\begin{overpic}[width =\figwid]{S1.pdf}\put(65,80){Start}
\end{overpic}
\begin{overpic}[width =\figwid]{S2.pdf}\put(50,80){Move 1}
\end{overpic}
\begin{overpic}[width =\figwid]{S3.pdf}\put(50,80){Move 2}
\end{overpic}
\begin{overpic}[width =\figwid]{S4.pdf}\put(50,80){Move 3}
\end{overpic}
\begin{overpic}[width =\figwid]{S5.pdf}\put(50,80){Move 4}
\end{overpic}
\begin{overpic}[width =\figwid]{S6.pdf}\put(50,80){Move 5}
\end{overpic}}\\

\caption{\label{fig:shapeControlMathematica1}{Frames from an implementation of Alg.\ \ref{alg:PosControl2Robots}: two robot positioning using walls with infinite friction. The algorithm only requires friction along the bottom and right walls.
Robot initial positions are shown by a square, and final positions by a circle.  Dashed lines show the shortest route if robots could be controlled independently.  Solid arrows show path given by  Alg.\ \ref{alg:PosControl2Robots}.
Online demonstration and source code at \citep{Shahrokhi2015mathematicaParticle}.
%The bottom row shows an extreme case where the robots must switch position.
}
\vspace{-1em}
}
\end{figure*}

@@

Assume two robots are initialized at $s_1$ and $s_2$ with corresponding goal destinations $e_1$ and $e_2$. 
We can exploit symmetry in the solution by labeling the leftmost  (or, if they have the same $x$ coordinate, the topmost) robot $s_1$.  If $s_1$ is not also the topmost robot, we rotate the coordinate frame by 90$^\circ$.
Denote the current positions of the robots  $r_1$ and $r_2$. 
Values $.x$ and $.y$ denote the $x$ and $y$ coordinates, i.e., $s_1.x$ and $s_1.y$ denote the $x$ and $y$ locations of $s_1$. Define the sign function as:
\begin{align}
\sign (x) = \begin{cases}  1, &  x > 0 \\
0, & x=0\\
-1, & x<0 \end{cases} 
\end{align}
The algorithm assigns a global control input at every instance.
The goal is to adjust 
 $\Delta r_x = r_2.x-r_1.x$ from $\Delta s_x = s_2.x-s_1.x$ to $\Delta e_x = e_2.x-e_1.x$ and  adjust 
 $\Delta r_y = r_2.y-r_1.y$ from $\Delta s_y = s_2.y-s_1.y$ to $\Delta e_y = e_2.y-e_1.y$ using a shared global control input. 
 This algorithm exploits the position-dependent friction model \eqref{eq:frictionmodel}.
 %employing the assumption we have made earlier about the walls' friction.

@@

\begin{algorithm}
\caption{GenerateDesiredSpacing($s_1,s_2,e_1,e_2,L$)}\label{alg:PosControl2Robots}
\begin{algorithmic}[1]
\scriptsize
\Require knowledge of starting $(s_1,s_2)$ and ending $(e_1,e_2)$ positions of  two robots. 
$(0,0)$ is bottom corner, $s_1$ is leftmost robot, 
 $L$ is length of the walls. Current robot positions are $(r_1,r_2)$.
 Assume $s_1.x < s_2.x$ and $s_1.y \geq s_2.y$. If not, rotate workspace coordinates $90^{\circ}$.
$\epsilon $ is a small, nonzero, user-specified value.

\Ensure $(e_1, e_2) , (s_1, s_2)$ all at least $\epsilon$ distance from walls.
\State $\Delta e_y = e_2.y - e_1.y$
\State $\Delta e_x = e_2.x - e_1.x$
\State Move $\left(-r_1.x , -\min \left(r_2.y , r_1.y+ \Delta e_y \right)+\epsilon \right)$ \Comment{Touch left wall}
%Second Move
%(-\min(|-r_2.x+ \Delta e_x|, r_2.x),
\State Move $ (r_2.x, |\sign(\Delta e_y)| \, \min(r_1.y - r_2.y + \Delta e_y-\epsilon,L-r_2.y-\epsilon)+ \epsilon)$
\Statex \Comment{Adjust  $y$}
%Third Move
\State Move $(\max(\epsilon, -\sign(r_2.y - r_1.y)\Delta e_x), -\min(r_1.y , r_2.y))$ 
\Statex \Comment{Touch bottom wall}
%Fourth Move
\State Move $(\sign(r_2.y - r_1.y)\Delta e_x , (|\sign(\Delta e_y)|-1) |r_2.y - r_1.y|)$ \Comment{Adjust $x$}
\If {$\Delta e_y \neq r_2.y - r_1.y$}
%Fifth Move
\If {$\Delta e_x \neq 0$}
\State Move $(\sign(r_2.y- r_1.y)\Delta e_x, |\sign(\Delta e_y)-1| |r_1.y-r_2.y|)$ \Comment{Touch right wall}
\Else
\State Move  $(|\sign(\Delta e_y -r_2.y+ r_1.y)| \epsilon, |\sign(\Delta e_y)-1| |r_1.y-r_2.y|)$ \Comment{Touch right wall}
\EndIf
%Sixth Move
\If {$\Delta e_x < 0$}
\State Move $(L - \max(r_1.x, r_2.x), \epsilon)$
\Else 
\State Move $(L - \max(r_1.x, r_2.x),\Delta e_y -\max(r_1.y, r_2.y)$ 
\Statex \Comment{Adjust $y$}
\EndIf
\EndIf
%Seventh Move
\State Move $(e_2.x - r_2.x, e_2.y - r_2.y)$ \Comment{Go to goal}
\end{algorithmic}
\end{algorithm}

>>>>

\begin{figure*}
\centering
\renewcommand{\figwid}{0.64\columnwidth}
{\begin{overpic}[width =\figwid]{RegionMove1.pdf}
\end{overpic}
\begin{overpic}[width =\figwid]{RegionMove2.pdf}
\end{overpic}
\begin{overpic}[width =\figwid]{RegionMove3.pdf}
\end{overpic}
}\\

\caption{\label{fig:regionMove}{Two rectangles representing the reachable regions for the current start and goal positions. The red square represents the starting $\Delta x$ and $\Delta y$ and the green circle represents the goal $\Delta x$ and $\Delta y$. The green rectangle illustrates one move reachable $\Delta x$ and $\Delta y$ by horizontal walls and the blue rectangle illustrates the vertical walls reachable region.
}
\vspace{-1em}
}
\end{figure*}

\section{Algorithms}\label{sec:algorithms}
\subsection{Position Control of Two Robots Using Wall Friction}\label{sec:PostionControl2Robots}
\begin{figure*}
\centering
\renewcommand{\figwid}{0.32\columnwidth}
{\begin{overpic}[width =\figwid]{story3Moves1.pdf}\put(65,80){Start}
\end{overpic}
\begin{overpic}[width =\figwid]{story3Moves2.pdf}\put(50,80){Move 1}
\end{overpic}
\begin{overpic}[width =\figwid]{story3Moves3.pdf}\put(50,80){Move 2}
\end{overpic}
\begin{overpic}[width =\figwid]{story3Moves4.pdf}\put(50,80){Move 3}
\end{overpic}
%\begin{overpic}[width =\figwid]{s5}\put(50,80){Move 4}
%\end{overpic}
%\begin{overpic}[width =\figwid]{S6.pdf}\put(50,80){Move 5}
%\end{overpic}
}\\
{\begin{overpic}[width =\figwid]{story5move0.pdf}\put(10,80){Start}
\end{overpic}
\begin{overpic}[width =\figwid]{story5move1.pdf}\put(10,80){Move 1}
\end{overpic}
\begin{overpic}[width =\figwid]{story5move2.pdf}\put(10,80){Move 2}
\end{overpic}
\begin{overpic}[width =\figwid]{story5move3.pdf}\put(10,80){Move 3}
\end{overpic}
\begin{overpic}[width =\figwid]{story5move4.pdf}\put(10,80){Move 4}
\end{overpic}
\begin{overpic}[width =\figwid]{story5move5.pdf}\put(10,80){Move 5}
\end{overpic}
}\\
{\begin{overpic}[width =\figwid]{story7move0.pdf}\put(65,80){Start}
\end{overpic}
\begin{overpic}[width =\figwid]{story7move1.pdf}\put(50,80){Move 1}
\end{overpic}
\begin{overpic}[width =\figwid]{story7move2.pdf}\put(50,80){Move 2}
\end{overpic}
\begin{overpic}[width =\figwid]{story7move3.pdf}\put(50,80){Move 3}
\end{overpic}
\begin{overpic}[width =\figwid]{story7move4.pdf}\put(50,80){Move 4}
\end{overpic}
\begin{overpic}[width =\figwid]{story7move5.pdf}\put(50,80){Move 5}
\end{overpic}
}\\

\caption{\label{fig:shapeControlMathematica1}{Frames from an implementation of Alg.\ \ref{alg:PosControl2Robots}: two robot positioning using walls with infinite friction. 
Robot start positions are shown by a square, and goal positions by a circle.  Dashed lines show the shortest route if robots could be controlled independently.  Solid arrows show path given by  Alg.\ \ref{alg:PosControl2Robots}.
Online demonstration and source code at \citep{Shahrokhi2015mathematicaParticle}.
%The bottom row shows an extreme case where the robots must switch position.
}
\vspace{-1em}
}
\end{figure*}

@@

Assume two robots are initialized at $s_1$ and $s_2$ with corresponding goal destinations $g_1$ and $g_2$. 
We can exploit symmetry in the solution by labeling the leftmost  (or, if they have the same $x$ coordinate, the topmost) robot $s_1$.  If $s_1$ is not also the topmost robot, we rotate the coordinate frame by 90$^\circ$ counterclockwise.
Denote the current positions of the robots  $r_1$ and $r_2$. 
Values $.x$ and $.y$ denote the $x$ and $y$ coordinates, i.e., $s_1.x$ and $s_1.y$ denote the $x$ and $y$ locations of $s_1$. Define the sign function as:
\begin{align}
\sign (x) = \begin{cases}  1, &  x > 0 \\
0, & x=0\\
-1, & x<0 \end{cases} 
\end{align}
The algorithm assigns a global control input at every instance.
The goal is to adjust 
 $\Delta r_x = r_2.x-r_1.x$ from $\Delta s_x = s_2.x-s_1.x$ to $\Delta e_x = e_2.x-e_1.x$ and  adjust 
 $\Delta r_y = r_2.y-r_1.y$ from $\Delta s_y = s_2.y-s_1.y$ to $\Delta e_y = e_2.y-e_1.y$ using a shared global control input. 
 %This algorithm exploits the position-dependent friction model \eqref{eq:frictionmodel}.
 %employing the assumption we have made earlier about the walls' friction.

@@

\begin{algorithm}
\caption{PoseControl2Robots($s_1,s_2,g_1,g_2,L$)}\label{alg:PosControl2Robots}
\begin{algorithmic}[1]
\scriptsize
\Require knowledge of starting $(s_1,s_2)$ and goal $(g_1,g_2)$ positions of  two robots. 
$(0,0)$ is bottom corner,
 $L$ is length of the walls. Current robot positions are $(r_1,r_2)$.
 Assume $s_1.x < s_2.x$ and $s_1.y \geq s_2.y$. If not, rotate workspace coordinates counterclockwise $90^{\circ}$.
$\epsilon $ is a small, nonzero, user-specified value.

\Ensure $(g_1, g_2) , (s_1, s_2)$ all at least $\epsilon$ distance from walls.
\State $\Delta g_y = e_2.y - e_1.y$
\State $\Delta g_x = e_2.x - e_1.x$
\State Move $\left(-r_1.x , -\min \left(r_2.y , r_1.y+ \Delta e_y \right)+\epsilon \right)$ \Comment{Touch left wall}
%Second Move
%(-\min(|-r_2.x+ \Delta e_x|, r_2.x),
\State Move $ (r_2.x, |\sign(\Delta e_y)| \, \min(r_1.y - r_2.y + \Delta e_y-\epsilon,L-r_2.y-\epsilon)+ \epsilon)$
\Statex \Comment{Adjust  $y$}
%Third Move
\State Move $(\max(\epsilon, -\sign(r_2.y - r_1.y)\Delta e_x), -\min(r_1.y , r_2.y))$ 
\Statex \Comment{Touch bottom wall}
%Fourth Move
\State Move $(\sign(r_2.y - r_1.y)\Delta e_x , (|\sign(\Delta e_y)|-1) |r_2.y - r_1.y|)$ \Comment{Adjust $x$}
\If {$\Delta e_y \neq r_2.y - r_1.y$}
%Fifth Move
\If {$\Delta e_x \neq 0$}
\State Move $(\sign(r_2.y- r_1.y)\Delta e_x, |\sign(\Delta e_y)-1| |r_1.y-r_2.y|)$ \Comment{Touch right wall}
\Else
\State Move  $(|\sign(\Delta e_y -r_2.y+ r_1.y)| \epsilon, |\sign(\Delta e_y)-1| |r_1.y-r_2.y|)$ \Comment{Touch right wall}
\EndIf
%Sixth Move
\If {$\Delta e_x < 0$}
\State Move $(L - \max(r_1.x, r_2.x), \epsilon)$
\Else 
\State Move $(L - \max(r_1.x, r_2.x),\Delta e_y -\max(r_1.y, r_2.y)$ 
\Statex \Comment{Adjust $y$}
\EndIf
\EndIf
%Seventh Move
\State Move $(e_2.x - r_2.x, e_2.y - r_2.y)$ \Comment{Go to goal}
\end{algorithmic}
\end{algorithm}
